### 2015-06-25 Manuscript/BiologyLetters/Table_results.tex
Word count massacre

\caption{Number of taxa with available cladistic data for mammalian orders at three taxonomic levels. The left vertical bar represents ``low'' coverage (\textless 25\%); the right vertical bar represents ``high'' coverage (\textgreater 75\%). A negative Net Relatedness Index (NRI) and Nearest Taxon Index (NTI) shows more phylogeneticaly dispersed taxa than expected by chance; a positive value shows more phylogeneticaly clustered taxa than expected by chance. Significant NRI or NTI values are highlighted in bold. One star (*) signifies a p-value between 0.05 and 0.005; two starts between 0.005 and 0.0005 and three stars \textless 0.0005.} \\ 

>>>>

\caption{Number of taxa with available cladistic data for mammalian orders at three taxonomic levels. The left vertical bar represents low coverage (\textless 25\%); the right vertical bar represents high coverage (\textgreater 75\%). Negative Net Relatedness Index (NRI) and Nearest Taxon Index (NTI) values indicate phylogenetic overdispersion; positive values indicate phylogenetic clustering. Significant NRI or NTI values are in bold. *p \textless 0.05; **p \textless 0.01; ***p \textless 0.001.} \\ 
